SBML L3 paper response to reviewers

### 2020-01-28 main.tex
Reemphasize reproducibility, per Andreas' suggestion
Minor word changes

The goal of the manuscript is to describe the possibilities that SBML offers, but we did not intend to gloss over difficulties or problems.  The manuscript already mentioned some related standards, and we have now tried to clarify the relationships better in the edited second paragraph of the section titled ``Impact of SBML''.  Since a comparison to other formats is not the focus of the paper, and the journal's paper guidelines have length limitations, we hope this compromise is good enough.  With respect to journals, we have added text to the manuscript mentioning journal and funding agency guidelines.  We have also added more discussions of difficulties involving SBML.  These changes are in the second-to-last paragraph of the section titled ``Impact of SBML'' and the last three paragraphs of the section titled ``Forthcoming challenges''.

@@

Thank you for raising this issue.  This is, unfortunately, a difficult point to address with SBML because its needs have been largely driven on demand in a bottom-up fashion, with proposals for features and packages coming when people felt the need or desire.  Consequently, we are not sure how to give explicit ``criteria for language standardization'' in the sense described above.  Nevertheless, we have added text to try to help address the issue: (a) in the introduction, we added text that mentions how SBML's popularity led to communities of modelers asking whether it could be expanded or adapted to more cases; and (b) in the section titled ``SBML Level 3's modularity and breadth'', the new fourth paragraph discusses benefits of building on SBML rather than creating a new format.

@@

These are important issues indeed.  In the revised manuscript, we have added text in the section titled ``Forthcoming challenges'' to acknowledge and touch upon some of the costs and benefits.  We feel that a more extended discussion of these topics has to be considered beyond the scope of this paper, but we hope that the new changes are enough to address the point to a reasonable extent.

>>>>

The goal of the manuscript is to describe the possibilities that SBML offers, but we did not intend to gloss over difficulties or problems.  The manuscript already mentioned some related standards, and we have now tried to clarify the relationships better in the edited second paragraph of the section titled ``Impact of SBML''.  Since a comparison to other formats is not the focus of the paper, and the journal's paper guidelines have length limitations, we trust that this compromise is good enough.  With respect to journals, we have added text to the manuscript mentioning journal and funding agency guidelines.  We have also added more discussions of difficulties involving SBML.  These changes are in the second-to-last paragraph of the section titled ``Impact of SBML'' and the last three paragraphs of the section titled ``Forthcoming challenges''.

@@

Thank you for raising this issue.  This is, unfortunately, a difficult point to address with SBML because its needs have been largely driven on demand in a bottom-up fashion, with proposals for features and packages coming when people felt the need or desire.  Consequently, we are not sure how to give explicit ``criteria for language standardization'' in the sense described above.  Nevertheless, we have added text to try to help address the issue: (a) in the introduction, we added text that mentions how SBML's popularity led to communities of modelers asking whether it could be expanded or adapted to more cases; and (b) in the section titled ``SBML Level 3's modularity and breadth'', the new fourth paragraph discusses benefits of building on SBML rather than creating a new format.  As part of these and other edits, we also reiterated that standard formats are important for reproducibility of scientific results, and thus are another reason to standardize around tool-agnostic formats like SBML.

@@

These are important issues indeed.  In the revised manuscript, we have added text in the section titled ``Forthcoming challenges'' to acknowledge and touch upon some of the costs and benefits.  We feel that a more extended discussion of these topics has to be considered beyond the scope of this paper, but we trust that the new changes are enough to address the point to a reasonable extent.
